Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-05 doc/JFLA2022/paper.tex
fix a typo in the abstract Put latex comments on several remaining TODOs. Move a paragraph in Section 2

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must continuously satisfied:
   maintenance of the library with respect to several \community projects it requires and evolutions of \coq, and 
  consistency of the book with respect to the library. 
\end{abstract}

@@

\TODO[Clément]{Could we use a font with ligatures?}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), lemmas (Fig.~\ref{fig:Ex42E0}), proof scripts (Fig.~\ref{fig:Ex42-schutte}), and computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}). The order in which these references appear in the book is independent of the structure of our libraries. Thus, we chose not to include our textbook as comments in the libraries (solution \emph{à la} Coqdoc).
\TODO[Pierre]{is the preceding sentence OK?}

Originally, we copied snippets from \coq sources into LaTeX manually, and recorded and inserted the corresponding outputs manually as well.  This approach is common, but brittle: changes to \coq definitions or lemmas had to be reflected in the book's sources, and we found multiple instances where the book and the \coq development had diverged. \TODO[Clément]{see FIXME cite alectryon for a discussion of various approaches to documentation of \coq developments}

>>>>

\begin{abstract}
  \Hydras is a collaborative library on discrete math, written for the \coq  proof assistant, and developed under the \community project. The proof scripts are
  accompanied with an electronic book, made with the help of the \alectr litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must be continuously satisfied:
   maintenance of the library with respect to several \community projects it requires and evolutions of \coq, and 
  consistency of the book with respect to the library. 
\end{abstract}

@@

%\TODO[Clément]{Could we use a font with ligatures?}

@@

The \Hydras book is written in LaTeX, but it makes very frequent references (about once per page, 274 snippets over 281 pages) to parts of the \coq development, showing definitions (Fig.~\ref{fig:Hprime}), lemmas (Fig.~\ref{fig:Ex42E0}), proof scripts (Fig.~\ref{fig:Ex42-schutte}), and computation results (Fig.~\ref{fig:Pow-evalPow17LetIn}). The order in which these references appear in the book is independent of the structure of our libraries. Thus, we chose not to include our textbook as comments in the libraries (solution \emph{à la} Coqdoc).
%\TODO[Pierre]{is the preceding sentence OK?}

Originally, we copied snippets from \coq sources into LaTeX manually, and recorded and inserted the corresponding outputs manually as well.  This approach is common, but brittle: changes to \coq definitions or lemmas had to be reflected in the book's sources, and we found multiple instances where the book and the \coq development had diverged. %\TODO[Clément]{see FIXME cite alectryon for a discussion of various approaches to documentation of \coq developments}
